---
title: "script1"
author: "Polong Lin & SangHee Park"
date: "December 6, 2014"
output: html_document
---
```{r}
knitr::opts_chunk$set(comment="", cache=TRUE)
```

## INIT
- Initiating working directory and dataset
- add "contribution_amount_dollars" column in dollars
```{r init}
setwd("/Users//polong//Documents/federal-contributions-analysis/munged_data/")
dataset <- read.csv("all_contributions_2004_to_2013.csv", stringsAsFactors = FALSE)
dataset$contribution_amount_dollars <- dataset$contribution_amount/100
source("postal_code_to_city.R")
head(dataset)

```

-remove negative and blank contributions
```{r remove}
nrow.before <- nrow(dataset)
dataset <- dataset[dataset$flag.negative_contrib == FALSE & 
                       dataset$flag.blank_contrib == FALSE,]
```
-`nrow(dataset) - nrow.before` rows with NEGATIVE or BLANK contribution amounts **removed**.

-set annual limits as a dataframe
```{r annuallimits}
annual_limits <- data.frame(c(5000, 1000, 1000, 1000),
                            c(5100, 1000, 1000, 1000),
                            c(1100, NA, NA, NA),
                            c(1100, NA, NA, NA),
                            c(1100, NA, NA, NA),
                            c(1100, NA, NA, NA),
                            c(1100, NA, NA, NA),
                            c(1100, NA, NA, NA),
                            c(1200, NA, NA, NA),
                            c(1200, NA, NA, NA),
                            c(1200, NA, NA, NA))
names(annual_limits) <- 2004:2014
rownames(annual_limits) <- c("Individuals","Corporations","Trade Unions","Assoc. 405.3(3)")
```

## Summary

```{r summary1}
summary(dataset)
```
###Results:
-n. observations: `nrow(dataset)`

## Create columns for year and month of donation
```{r year}

dataset$contribution_date.adjusted <- as.Date(dataset$contribution_date.adjusted, "%Y-%m-%d")


dataset$year <- as.numeric(format(dataset$contribution_date.adjusted, "%Y"))
head(dataset$year)

dataset$month <- as.numeric(format(dataset$contribution_date.adjusted, "%m"))

dataset$day <- as.numeric(format(dataset$contribution_date.adjusted, "%d"))

```


## Donations by date, plotted
```{r donations_by_date}
dataset$contribution_amount_dollars <- dataset$contribution_amount/100
don_per_party_by_date <- aggregate(contribution_amount_dollars ~ year + month + day + party_name, dataset, sum)

#don_per_party_by_date$date <- as.Date(format(as.Date(don_per_party_by_date, "%Y %m %d")))

require(ggplot2)
ggplot() + 
  coord_cartesian() +
  scale_x_continuous() +
  scale_y_continuous() +
  scale_color_hue() +
  #facet_wrap(~party_name) +
  layer(
    data=don_per_party_by_date, 
    mapping=aes(x=year, y=contribution_amount_dollars/1000, color=party_name), 
    stat="identity", 
    stat_params=list(), 
    geom="line", 
    geom_params=list(), 
    position=position_jitter()
  )

```


## Removing event-based donations

### Removing Year-End donations (December 31)
```{r yearend}
don_per_party_by_date <- don_per_party_by_date[don_per_party_by_date$month != 12 & don_per_party_by_date$day != 31,]

ggplot() + 
  coord_cartesian() +
  scale_x_continuous() +
  scale_y_continuous() +
  scale_color_hue() +
  facet_wrap(~party_name) +
  layer(
    data=don_per_party_by_date, 
    mapping=aes(x=year, y=contribution_amount_dollars/1000, color=party_name), 
    stat="identity", 
    stat_params=list(), 
    geom="line", 
    geom_params=list(), 
    position=position_jitter()
  )

head(don_per_party_by_date[order(don_per_party_by_date$contribution_amount_dollars, decreasing = TRUE),], n = 20)

dataset[dataset$full_name == "Gordon Rawlinson",]


```


## Donations by amount

```{r donations_by_amt}

require(ggplot2)
ggplot() + 
  coord_cartesian() +
  scale_x_continuous() +
  scale_y_continuous() +
  scale_color_hue() +
  facet_wrap(~party_name) +
  layer(
    data=don_per_party_by_date, 
    mapping=aes(x=month, y=contribution_amount_dollars/1000, color=party_name), 
    stat="identity", 
    stat_params=list(), 
    geom="line", 
    geom_params=list(), 
    position=position_jitter()
  )
```

## Donations per postal code per day

```{r donations}
head(dataset)

donations_by_postal_by_day <- aggregate(dataset$contribution_amount_dollars ~ dataset$postal_code + dataset$contribution_date.adjusted + dataset$party_name, dataset, sum)
num_donations_by_postal_by_day <- aggregate(dataset$contribution_amount_dollars ~ dataset$postal_code + dataset$contribution_date.adjusted + dataset$party_name, dataset, length)

head(donations_by_postal_by_day)
head(num_donations_by_postal_by_day)

head(donations_by_postal_by_day)



donations_by_postal_by_day <- merge(donations_by_postal_by_day, num_donations_by_postal_by_day, by = c("dataset$postal_code", "dataset$contribution_date.adjusted", "dataset$party_name"))

names(donations_by_postal_by_day) <- c("postal_code", "contribution_date.adjusted", "party_name", "contrib_amount_dollars", "n_contributions")

#boxplot(donations_by_postal_by_day$n_contributions)

summary(donations_by_postal_by_day)

head(donations_by_postal_by_day[order(donations_by_postal_by_day$n_contributions, decreasing = TRUE),], 
     n = 20)

plot(donations_by_postal_by_day$contrib_amount_dollars, donations_by_postal_by_day$n_contributions,
     ylab = "# of Contributions", xlab = "Total Contrib per day, PC, party")

```

## Look at the maximum donators - what are they doing?

Generate list of "maxers":
```{r maximum_donators}

dataset_maxers <- rbind(dataset[dataset$year == 2004 & dataset$contribution_amount_dollars == 5000,], 
                        dataset[dataset$year == 2005 & dataset$contribution_amount_dollars == 5100,],
                        dataset[dataset$year == 2006 & dataset$contribution_amount_dollars == 5200,],
                        dataset[dataset$year > 2007 & dataset$year < 2012 & dataset$contribution_amount_dollars == 1100,],
                        dataset[dataset$year > 2011 & dataset$contribution_amount_dollars == 1200,])

```


## Top Overall Contributors by name
```{r donations_by_name}
don_by_name <- aggregate(contribution_amount_dollars ~ full_name, dataset, sum)

head(don_by_name[order(don_by_name$contribution_amount_dollars, decreasing = TRUE),], n = 50)

```

## Remove over-limit donations
-remove year-end donations
```{r removing_overlimit_donations}
dataset_within_limit <- rbind(dataset[dataset$year == 2004 & dataset$contribution_amount_dollars <= 5000,], 
                        dataset[dataset$year == 2005 & dataset$contribution_amount_dollars <= 5100,],
                        dataset[dataset$year == 2006 & dataset$contribution_amount_dollars <= 5200,],
                        dataset[dataset$year >= 2007 & dataset$year <= 2011 & dataset$contribution_amount_dollars <= 1100,],
                        dataset[dataset$year > 2011 & dataset$contribution_amount_dollars <= 1200,])

don_within_limit <- aggregate(contribution_amount_dollars ~ year + month + day + party_name, dataset_within_limit, sum)

don_within_limit <- don_within_limit[don_within_limit$month != 12 & don_within_limit$day != 31,]



require(ggplot2)
ggplot() + 
  coord_cartesian() +
  scale_x_continuous() +
  scale_y_continuous() +
  scale_color_hue() +
  facet_wrap(~party_name) +
  layer(
    data=don_within_limit, 
    mapping=aes(x=year, y=contribution_amount_dollars/1000, color=party_name), 
    stat="identity", 
    stat_params=list(), 
    geom="line", 
    geom_params=list(), 
    position=position_jitter()
  )

```

Outlier days:
```{r outlierdays}
don_within_limit[don_within_limit$contribution_amount_dollars > 400000,]
```

On November 30, 2006, there were `r nrow(dataset_within_limit[dataset_within_limit$date == "2006-11-30"& dataset_within_limit$contribution_amount_dollars == "919.98",])` contributions of exactly $919.98. High profile supporters[edit]
"Former New Brunswick Premier Frank McKenna, considered the leading contender until he announced he was not running in the race, had donated $3000 to Brison's campaign in August and formally endorsed Brison on November" (http://en.wikipedia.org/wiki/Liberal_Party_of_Canada_leadership_election,_2006)

